Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-11 tex/MISDP-Presolving/MISDPpresolving.tex
add part on convex hulls for RIP

@@

\paragraph{Two Valid SOCP Constraints}

>>>>

\begin{question}
  One idea is to perform spatial branching on the diagonal entries
  $X_ii$. Does this help to solve the problem?
\end{question}

\subsubsection{Complete Description of Feasible Set}

One interesting question is whether one can describe the convex hull of the
feasible set. For this define
\begin{align*}
  S = \Big\{(X,z) \in S^n_+ \times [0,1]^n \suchthat & \tr(X) = 1,\; \sum_{i=1}^n z_i \leq k,\;     0 \leq X_{ii} \leq z_j \;\forall\, i \in [n],\\
                                                     & -\tfrac{1}{2} z_j \leq X_{ij} \leq \tfrac{1}{2} z_j \;\forall\, i \neq j \in [n] \Big\},
\end{align*}
which is the strongest relaxation that we currently have. Its integer hull is
\begin{align*}
  S_I \define \conv \Big\{& (X,z) \in S^n_+ \times \{0,1\}^n \suchthat \tr(X) =
                1,\; \sum_{i=1}^n z_i \leq k,\; 0 \leq X_{ii} \leq z_j \;\forall\, i \in [n] \Big\}.
\end{align*}
In general, we have $S \neq S_I$: If $k = 1$, then all off-diagonals have
to be zero in $S_I$, but not necessarily in~$S$. Moreover, consider
$2 \leq k \leq n$. Then for
\[
  z = \begin{pmatrix}
    \tfrac{1}{k} \\
    \vdots\\
    \tfrac{1}{k}
  \end{pmatrix},\quad
  X \define
  \begin{pmatrix}
    \tfrac{1}{k} & \dots, & \tfrac{1}{k}\\
    \vdots & \ddots & \vdots\\
    \tfrac{1}{k} & \dots & \tfrac{1}{k}
  \end{pmatrix},
\]
we have $(X,z) \in S$, but $(X,z) \notin S_I$.

\paragraph{Linear Case}

It might be instrumential to look at the linear analogue:
\[
  S \define \{(x,z) \in \R_+^n \times [0,1]^n \suchthat \sum_{i=1}^n x_i =
  1,\; \sum_{i=1}^n z_i \leq k,\; 0 \leq x_i \leq z_i \;\forall\, i \in [n]\}.
\]
This is related to the \emph{hypersimplex}
\[
  \Delta_{n,k} \define \conv \{z \in \{0,1\}^n \suchthat \sum_{i=1}^n z_i = k\},
\]
for which complete linear descriptions are available, see
Ziegler~\cite{Zie95}.

\begin{question}
  Does this give a linear description of $S$ and can this be extended to
  the SDP case?
\end{question}

\subsubsection{Nonnegativity by the Perron-Frobenius Theorem}

@@

\subsubsection{Two Valid SOCP Constraints}
